### 2024-04-29 thesis/input_files/problemdescription.tex
comm 1.4

\section{Outline}
We start with a literature review and bibliometric analysis in section \ref{literature_review}.
Then the theory underlying kernel methods is covered in section \ref{kernel_theory}. Following, section \ref{state_of_the_art} introduces the state of the art methods in the context of both point and probabilistic forecasting. Section \ref{energy_market} explains the core features and terminology of the energy market and of the electricity newtork.
Evaluation metrics necessary to rank the forecasting techniques are presented in section \ref{metrics}. Section \ref{eda} goes on with the ETL pipeline and the exploratory analysis. 
Implementation details are included in \ref{implementation}.
Finally section \ref{experiments} presents the experiments, the results and discusses models' strenghts, weaknesses and possible improvements.

>>>>

\section{Outline}
We start with a literature review and a bibliometric analysis in Section \ref{literature_review}.
Then, the theory underlying kernel methods is covered in Section \ref{kernel_theory}. Evaluation metrics necessary to rank the forecasting techniques are presented in Section \ref{metrics}. Section \ref{energy_market} explains the core features and terminology of the energy market and of the electricity newtork.
Following, Sections \ref{ch:point} and \ref{ch:prob} introduce the state of the art methods in the context of point and probabilistic forecasting respectively.
Section \ref{eda} goes on with the etract-load-transform (ETL) pipeline and the exploratory analysis (EDA). 
Implementation details are included in \ref{implementation}.
Finally, section \ref{analysis} presents the experiments, the results and discusses models' strenghts, weaknesses and possible improvements.
